%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {MLAT Team Lead / Senior Programmer} % Job title
    {Passur Aerospace Inc.} % Organization
    {Orlando, FL} % Location
    {2010 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented fusing of aircraft flight plan data from many data sources providing unique id's and combined data.}
        \item {Team Lead on an 18 month Navy Small Business Innovation Research (SBIR) Contract for ML/AI anomaly detection in flight data.}
        \item {Designed, prototyped, coded an aircraft surface multilateration system (MLAT) deployed at 7 airports in the US.}
	\item {Implemented a multithreaded SDR decoder processing 100MB/sec with nanosecond timestamping of signal for MLAT (Ettus USRP UHD API).}
        \item {Implemented a load balanced backend for incoming MLAT data including a Redis sentinel failover cluster.}
        \item {Implemented a multithreaded MLAT location solver including Kalman filtering to smooth the aircraft tracks.}
        \item {Designed and implemented algorithms for detecting aircraft holding patterns and diversions from aircraft tracks.}
        \item {Designed and implemented fusing of disparate aircraft radar data into a continuous flight track while excluding incorrect data.}
        \item {High performance HTTP and socket programming for real time data updates to web browser (eventually replaced by Websockets).}
        \item {Designed a probability based method for correlating aircraft tail and flightid to mitigate incorrect data.}
        \item {Designed and maintained PostgreSQL databases of flight data.}
        \item {Promoted use of Git source control; migrated company source code to locally hosted Gitlab and CI/CD pipeline.}
        \item {Collected disparate software projects into git with a cohesive build system.}
        \item {Lead successful migration of software stack to an Orlando Datacenter.}
        % \item {}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Programmer} % Job title
    {Innovative Routines International Inc.} % Organization
    {Melbourne, FL} % Location
    {2000 - 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Team Lead on CoSort product; a high performance, high volume sort/merge/join/conversion tool used by large corporations and banks.}
        \item {Pushed migration to CVS source code control and autoconf build system to automate multiplatform builds.}
        \item {Designed and implemented modern thread-safe multithreaded version.}
        \item {Analyzed and implemented performance improvements and multithreaded algorithms.}
        \item {Designed and implemented module/dll loading functionality; implemented ODBC DB access module.}
        \item {Designed and implemented support for Unicode and double byte character sets.}
        \item {Designed and implemented scripting language conversion utilities.}
        \item {Performed regular customer support and debugging, often remotely; visited customers on occasion.}
        \item {Set up and maintained company internet firewall, ftp, and email servers (Linux).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {Computer Science Lab} % Job title
  {Florida Institute of Technology (Florida Tech)} % Organization
  {Melbourne, FL} % Location
  {1997 - 1998} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Tutored students on Computer Science assignments.}
      \item {Competed in ACM's International Programming Contest.}
    \end{cvitems}
  }

%---------------------------------------------------------
%  \cventry
%    {Tech Support} % Job title
%    {Internet Access \& Web Services of Florida (merged into atlantic.net)} % Organization
%    {Mt. Dora, FL} % Location
%    {1997} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Customer support; built and repaired computers}
%        \item {Implemented and administered a NewNet IRC server}
%      \end{cvitems}
%    }

%---------------------------------------------------------
\end{cventries}
